\section{Introduction}
\setresponsible{Regen Wijaya}
The meat-processing industry generates large quantities of organic residue that are difficult to dispose of and pose a risk to soil and water if they are left untreated. Anaerobic digestion is one established route for handling this material: micro-organisms break it down in the absence of oxygen and release biogas, a methane-rich fuel. What remains afterwards is digestate, a wet slurry that still carries most of the nitrogen, phosphorus and other nutrients of the original feedstock. Digestate is usually spread on farmland, but its high water content, variable composition, and the cost of transporting and storing it limit how much can be used in this way \parencite{tambone-2010}. The residue of a recycling process, therefore, becomes a waste problem of its own.

Pyrolysis turns that residue into a more stable and more useful solid. Heating the dried digestate in an oxygen-limited atmosphere drives off the volatile fraction and leaves a porous, carbon-rich material called biochar \parencite{Qi2024}. Biochar can be returned to the soil, where it improves structure, holds water and nutrients, and stores carbon for long periods \parencite{Lehmann2015}; with further treatment it can also act as a porous adsorbent for removing contaminants from gases and liquids. It is combustible as well, and so has some value as a solid fuel, but that is a secondary consideration in the present work.

Most of what is known about biochar comes from wood and crop feedstock. Digestate-derived biochar, and slaughterhouse digestate in particular, has received far less attention, even though its mineral-rich composition makes it behave quite differently from lignocellulosic char \parencite{opatokun-2015}. A further practical point is that the digestate studied here arrived without any supplier specification of its composition, which is why its elemental make-up is determined in-house rather than taken from a data sheet.

The slaughterhouse case closes a loop. Anaerobic digestion of slaughterhouse waste produces biogas contaminated with hydrogen sulfide (H$_2$S), a toxic and corrosive gas that has to be removed before the biogas can be used \parencite{salminen-2002}. Activated biochar made from the digestate can adsorb that H$_2$S and convert it to elemental sulfur on its surface. The result is a sulfur-enriched biochar that can then be applied to soil, where sulfur serves as a plant nutrient \parencite{Zhang2017SulfurEnrichedBiochar}. A single feedstock thus addresses two problems at once: the digestate is diverted from disposal, and the H$_2$S is stripped from the biogas, with both ending up in a material that returns nutrients to the field.

This thesis examines that route experimentally. It builds on an earlier Projektarbeit in which biochar was produced from three digestate types, namely bio-waste, grass silage and slaughterhouse residue, and activated under carbon dioxide \parencite{MartinezHuete2024Projektarbeit}. Two changes define the present study. Activation is carried out with steam (H$_2$O) rather than CO$_2$, and the calorific value of the char is measured directly by bomb calorimetry, a method that was not used in the earlier work. Slaughterhouse digestate of French origin is the main feedstock, while a comparable Algerian digestate provides a second dataset against which the French results are read. Where they are relevant, the earlier CO$_2$-activation results are drawn into the discussion rather than presented as a separate chapter.


\subsection{Objectives of The Work}

\subsubsection{General Objective}

The general objective of this work is to explore the potential of different digestates from slaughterhouse for biochar production, including its potential modification through activation and sulfur loading. This work investigates the effect of pyrolysis temperature on the biochar production, the effect of steam as activating agent on biochar activation, and the feasibility of sulfur enrichment on the resulting biochars. This works also aims to characterize the properties of the resulting biochars. 

\subsubsection{Specific Objectives}

To help in achieving the overall objectives of this work, several specific objectives are formulated. These are as follows:

\begin{itemize}
    \item to produce biochar from two different slaughterhouse digestate using pyrolysis with temperatures at 400, 500, and 600~$^\circ$C, and further determine the yield obtained at each temperature. The higher heating value of the char is also determined by bomb calorimetry as a complementary fuel property 
    \item to perform the activation of biochars with steam and to quantify the effect of activation through the associated mass loss.
    \item to carry out the sulfur-loading process on the activated biochars with sulfur-rich compound and to asses it suitability as soil amendment in agricultural application. 
    \item to characterize the physicochemical of the resulting biochars using several methods, including BET surface area analysis, scanning electron microscopy with EDX, and CHNS elemental analysis.  
    \item to compare the French and Algerian feedstocks, and to set the findings against the CO$_2$-activation baseline of the earlier Projektarbeit.
\end{itemize}

\subsubsection{Limitation of Work}

In this work, several limitations were encountered, particularly in the pyrolysis and steam activation experiments. Firstly, the amount of produced biochars are limited due to limited amount of biomass/feedstock available to undergo pyrolisis. This could affect further experiments that need a big amount of biochars. A further limitation concerned the steam activation system, in particular the reactor tube and the vessel, which were not in perfect condition. Furthermore, it was not possible to install a suitable water pipe connected directly to the reactor, as this would have been too time-consuming. Therefore, the water was introduced into the reactor using single-use syringe, which may have meant that the activation process did not proceed quite as it should have.  

\vspace{0.8em}

\newpage
Limitation was also encountered to analyze or characterize the resulting biochars. Analysis or characterization methods such as BET surface area analysis, scanning electron microscopy with EDX, and CHNS elemental analysis, had to be outsoruced and were relatively expensive, only several samples of biochars were selected. 

\subsection{Structure of The Thesis}

The thesis is structured into several chapters, each of which covers specific aspect of the research that together outline the overall framework of this work as follows:

\vspace{0.8em}

The \textbf{chapter~1} introduces the context of the work, consisting of research background, objectives, and strcuture of the thesis.

\vspace{0.8em}

The \textbf{chapter~2} presents the theoretical background of the work, serving as basic principles for the experiment and analysis. 

\vspace{0.8em}

The \textbf{chapter~3} outlines the experimental investigations that carried out within the scope of this work, covering the materials as well as methods for the experiment. 

\vspace{0.8em}

The \textbf{chapter~4} presents the result of the experiments. The result is interpreted to highlight the key findings related to the overall objectives of this thesis.