\newpage
\section{Results}



\subsection{Pyrolyse for Biochar production}
The biochar yield was determined gravimetrically for both the French and the Algerian slaughterhouse digestate at 400, 500, 600\,°C. To accomodate the limited quantity of available material, each digestate portion was divided across three crucibles and pyrolysed under identical conditions (heating rate
10\,°C\,min$^{-1}$, residence time 1\,h, with the crucible water held at
approximately 20\,g in every run to maintain a comparable steam environment). The three crucibles act as replicates, and the values reported in Table~\ref{tab:pyrolysis-yield} are the mean of the three measurements. Yield is expressed as the ratio of recovered biochar to the as-received digestate charge.

\begin{table}[ht]
\centering
\caption{Biochar yield (mean of three crucible replicates $\pm$ standard
deviation) for the French and Algerian slaughterhouse digestate at three
pyrolysis temperatures. Heating rate 10\,°C\,min$^{-1}$, residence time 1\,h.}
\label{tab:pyrolysis-yield}
\begin{tabular}{ccc}
\toprule
Pyrolysis temperature (°C) & French yield (\%) & Algerian yield (\%) \\
\midrule
400 & $45.75 \pm 0.04$ & $37.42 \pm 0.26$ \\
500 & $43.12 \pm 0.04$ & $34.37 \pm 0.11$ \\
600 & $42.18 \pm 0.05$ & $33.45 \pm 0.48$ \\
\bottomrule
\end{tabular}
\end{table}

Both feedstocks behave consistently within each run, with the replicate standard deviation staying below half a percentage point throughout. Across the temperature range, the French digestate returns the higher solid yield, falling from 45.7\,\% at
400\,°C to 42.2\,\% at 600\,°C, whereas the Algerian digestate yields between
37.4\,\% and 33.5\,\% over the same interval. The french char therefore exceeds the Algerian by roughly eight to nine percentage points at every temperature.

Since both substrates were derived from slaughterhouse waste and were also assumed processed under identical conditions, this difference is attributable to feedstock composition. The consistently higher French yield reflects a larger fraction of material retained in the solid phase, which points to differences in the organic and mineral balance of the two digestates arising from their respective origins and upstream digestion. The interpretation is taken up again against the elemental and ash data in Section~\ref{sec:characterisation}, where the mineral content recovered in the char is quantified directly.

Both digestates show a steady decrease in yield as the pyrolysis temperature rises, amounting to about 3.6 percentage points for the French and 4.0 for the Algerian material between 5-- and 600\,°C. The downward trend follows the expected release of volatile matter at higher temperature, as the more thermally labile fractions are driven off and a more carbonised residue remains (Section~\ref{subsubsec:Effect of Temperature on Biochar}). The not-so-steep decline is itself informative: in digestate-derived feedstocks the high mineral fraction is largely retained in the solid during pyrolysis, so the yield responds less steeply to temperature than is 
\subsection{\texorpdfstring{H$_2$O}{H2O}-Activation}



\subsection{Sulfur Loading}


\subsection{Characterization of biochar}

\subsubsection{CHNS Elemental Analysis}

\subsubsection{SEM-Analysis}

